### 2008-03-06 trunk/SAiP/Module1/H3/doc/softwarearchitecture.tex
Adding first part of Perry&Wolf

>>>>

Perry and Wolf suggest seperating the model of the architecture into three components, as mentioned in the question. The components relate in the sense that the \emph{elements} has a particular \emph{form} and them and their relations are chosen based on a \emph{rational}.

There are three class of architectual elements defined.
\begin{itemize}
    \item[Processing elements] Transforms data elements.
    \item[Data elements] Information to be transformed or used.
    \item[Connecting elements] The \emph{glue} that hold the architecture together. May at times be \emph{Data elements}, \emph{Connecting elements} or both. The connecting elements are the relations between the different elements, e.g. procedure calls or message parsing.
\end{itemize}

The architectual form describe the architectual properties and the relationships and their relative importance. This is important as some architectual properties
may be vital to the design and others may be gold-plating. These properties are used to put constraints on the elements and also define the relative importanse of these constraints. The relationships are similar to the properties except they are used to put constraints and relative priority on the relations between elements.

A software architecture is a selection and description of architectual choices. These choices are, however, difficult to convay without including the reason for the choices made, for the elemenents and form not chosen and for choices not made due to lack of information or because they were deemed irrelevant.

When the above is applied to the information present for the Beer Web Store three processing elements, one data element and two connecting elements may be defined. These are as follow:

\begin{itemize}
    \item Processing elements.
	 \begin{itemize}
	    \item[Client]
	    \item[Server]
	    \item[DatabaseFacade]
	 \end{itemize}
    \item Data elements.
	 \begin{itemize}
	    \item[Request data]
	 \end{itemize}
    \item Connecting elements.
	 \begin{itemize}
	    \item[HTTP]
	    \item[Database facade methods]
	 \end{itemize}
\end{itemize}
